### 2020-06-14 implementation.tex
removed irrelevant files

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset. Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Fig~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}

>>>>

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset. Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Fig~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}
